Regular singular Volterra equations on complex domains

### 2024-05-02 sima/reg-sing-volterra_sima.tex
Reorganize proof of `thm:example`

@@

The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$. With stronger constraints on $\hardpart$, \textcolor{red}{we can also ensure} \textcolor{brown}{it is guaranteed} that $\solproto$ grows at most exponentially as $|\zeta| \to \infty$. The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
%\textcolor{Tomato}{If we change Condition \eqref{cond:sing}, it'll be enough to assume Condition \eqref{cond:diag-basic} to state Theorem \ref{thm:proto-growth}.}
\begin{theorem}\label{thm:proto-growth}
Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.

Suppose $\hardpart$ also satisfies {\em Condition~\eqref{cond:diag-basic}}. Then $f_0$ belongs to the space $\singexpalg{\tau-1}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{theorem}
We will prove this result in Section~\ref{sec:asymptotics}.
\begin{rmk}
When $\hardpart$ also satisfies Condition~\eqref{cond:reg-p}, we can get a better estimate of the prototype solution near $\zeta = 0$, as described in Proposition~\ref{prop:better-proto-estimate} from Section~\ref{sec:asymptotics}.
\end{rmk}
%
\textcolor{red}{When we perturb $\hardpart$ to the more general operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed}, the equation we are trying to solve gets more complicated} \textcolor{brown}{For the pertubed operator $\volterra=\hardpart+\softpart$, the equation $f=\volterra f$ is more complicated}, but its regular singularity at $\zeta = 0$ \textcolor{violet}{stays [make previous part of sentence consistent]} essentially the same. We might therefore expect to find a solution that looks like $\solproto$ near the singularity, differing only by a less singular perturbation. If we strengthen the constraints on $\hardpart$ a little more, this expectation is fulfilled.
\begin{theorem}\label{thm:general_volterra}
Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}. Then the equation
\[ f = \volterra f \]
has a unique solution $f$ in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\gamma}(\Omega) \]
of the space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the space $\singexpalg{\tau-1}(\domain)$.

@@

Now, using Condition~\eqref{cond:sing} again, \textcolor{red}{choose some $\sigma > \tau$ and find a radius $r < \delta$} for a given $\sigma>0$ there exists a radius $r<\delta$ for which
\[ \left|\frac{q(a')}{p(a)}\right| < \frac{\sigma}{|\zeta(a)|} \]
whenever $|\zeta(a)| < r$ and $|\zeta(a')| < r$. Choosing a point $b'$ with $|\zeta(b')| < r$ and $q(b') \neq 0$, we \textcolor{red}{can} deduce that
\begin{align*}
|\solproto| & \lesssim \left|\frac{1}{q(b')}\right|\,\left|\frac{q(b')}{p}\right|\,|\zeta|^\tau \\
& \lesssim \left|\frac{1}{q(b')}\right|\,\frac{\sigma}{|\zeta|}\,|\zeta|^\tau \\
& \lesssim |\zeta|^{\tau-1}
\end{align*}
on the region $|\zeta| < r$, as desired.
\end{proof}
\begin{proposition}\label{prop:asymptotic at infinity}
Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}. Then $\solproto$ belongs to the space $\singexpalg{\tau-1}(\domain)$.
\end{proposition}
\begin{proof}
We want to show that $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ for some real constant $\lambda_0$.

@@

Now, let us look at the exponential factor. By Condition~\eqref{cond:sing}, \textcolor{red}{we can find} \textcolor{brown}{there exist} a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
\[ \left| \frac{q}{p}+\frac{\tau}{\zeta} \right| < C \]
in $\domain_\text{near}$. It follows that the improper integral
\[ \eta(a) = \int_{\zeta = 0}^a \left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta \]
converges for all $a \in \domain$, allowing us to write
\[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] = e^{\eta(b)} e^{-\eta(a)}. \]
Observing that $|\eta| \le C |\zeta|$ in $\near$, we conclude that
\[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] \in e^{\eta(b)} \Big[ 1 + O\big(|\zeta(a)|\big) \Big] \]
at $\zeta(a) = 0$.

@@

Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:diag-basic}}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}. Choose a subset $\far \subset \domain$ that does not touch $\zeta = 0$.\footnote{\textcolor{red}{A subset of a topological space {\em touches} the points in its closure~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.}} Then, for any $\lambda > \lambda_\Delta$, we have

@@

Let us again use the straight integration path $\zeta = t \zeta(a)$, with $t \in (0, 1]$. Along this path, $|\zeta(a) - \zeta| = |\zeta(a)| - |\zeta|$, allowing us to combine the exponential factors in our bound:

@@

Let us set $\Lambda > \lambda$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows. Then \textcolor{red}{we can make our bound uniform} \textcolor{brown}{there is an uniform bound} over all $a \in \far$, since $|\zeta(a)| \ge \delta$ for these points:

@@

\textcolor{red}{Now, we just want to} \textcolor{brown}{Next, we} show that the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$ for any $\rho > \tau$.

First, suppose $\rho \in (\tau, \tau+\gamma)$. In this case, we \textcolor{red}{can} use the inclusion $\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} to see that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$. Lemma~\ref{lem:perturbed_volterra} then guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found in $\singexpalg{\tau-1+\gamma}(\Omega)$.

On the other hand, suppose $\rho > \tau+\gamma$. In this case, Proposition~\ref{prop:inclus-lt-pow-alg} gives an inclusion $\singexpalg{\rho-1}(\Omega) \hookrightarrow \singexpalg{\tau-1+\gamma}(\Omega)$. Under this inclusion, any solution of Equation~\eqref{eqn:equiv-inhomog} that we might find in $\singexpalg{\rho-1}(\Omega)$ must match the unique solution we found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
\end{proof}
\color{blue}\begin{proposition}\label{prop:alt-general_volterra}
Suppose $\volterra$ satisfies {\em Condition~\eqref{cond:reg-p}} in addition to the other assumptions of {\em Theorem~\ref{thm:general_volterra}}. Then, for each $\rho \in (\tau,\;\tau + \min\{\gamma, \epsilon, 1\}]$, the equation
\[f = \volterra f\]
has a unique solution $f$ in the affine subspace
\[ \zeta^{\tau-1}+\singexpalg{\rho-1}(\domain) \]
of the space $\singexpalg{\tau-1}(\domain)$.
\end{proposition}\color{black}
\begin{proof}
Propositions \ref{prop:asymptotic at infinity} and \ref{prop:better-proto-estimate} imply that for some constant $M$,
\[ \zeta^{\tau-1} + \singexpalg{\rho-1}(\domain) = M^{-1}\solproto + \singexpalg{\rho-1}(\domain) \]
whenever $\rho \le \tau + \min\{\epsilon, 1\}$. Theorem~\ref{thm:general_volterra} implies that our equation has a unique solution in
\[ M^{-1}\solproto + \singexpalg{\rho-1}(\domain) \]
as long as $\rho \in (\tau, \tau + \gamma]$. Putting these facts together, we get the desired result.
\end{proof}
\section{A motivating example}\label{sec:example}
\subsection{Overview}
We \textcolor{red}{can use our understanding of} use regular singular Volterra equations to study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$. In particular, we \textcolor{red}{can} build a set of analytic solutions in the frequency domain by solving certain regular singular Volterra equations in the position domain. Our main results guarantee that these position domain solutions exist, are unique, and have well-defined Laplace transforms.
\subsection{Level $1$ differential equations}\label{sec:level 1 ODE}
Let $\mathcal{P}$ be a linear differential operator of the form
\[ \mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}), \]
where
\begin{enumerate}
\item[$\bullet$] $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial that is non-zero at every root of $P$;
\item[$\bullet$] $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
\[ R(z^{-1}) = \sum_{j=0}^\infty R_j z^{-j} \]
converges in the region $|z| > A$.
\end{enumerate}
Equations of the form $\mathcal{P}\Phi = 0$ are a sub-class of what Ecalle calls {\em level~1} differential equations~\cite[Section~2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}. In an upcoming paper \cite{borel_reg}, we will study various examples of such equations using Laplace transform methods, with the help of our existence and uniqueness result Theorem~\ref{thm:general_volterra}. 
\subsection{Notation}\label{sec:notation_alpha}
So far, we have studied a Volterra equation with a regular singularity at $\zeta = 0$. When we use Laplace transform methods to solve a level~1 differential equation $\mathcal{P}\Phi = 0$ in the frequency domain, we will end up with several Volterra equations $\hat{\mathcal{P}}_\alpha \varphi = 0$ in the position domain, each with a regular singularity at a different root $\zeta = \alpha$ of the polynomial $P(-\zeta)$.

@@

\begin{rmk}
In the relationship between $\fracderiv{-\nu}{\zeta}{\alpha}$ and multiplication by $z^{-\nu}$ described above, smoothing out the singularity at $\zeta = \alpha$ in the position domain corresponds to speeding up the decay as $|z| \to \infty$ in the frequency domain. This is a general feature of the Laplace transform.
\end{rmk}
\subsection{Going to the position domain}
Using the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ \textcolor{red}{we can turn} \textcolor{brown}{differential operators in the frequency domain become} \textcolor{red}{into} Volterra operators in the position domain. 
\begin{lemma}\label{lem:use-dict}
\textcolor{cyan}{For each root $-\alpha$ of $P$} \textcolor{brown}{For each $\alpha\in\C$}, let $\hat{\mathcal{P}}_{\alpha}$ be the Volterra operator 
\color{cyan}\[ \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1}). \]
\color{brown}
\begin{equation}\label{eq:hat-P-alpha}
    \big[\hat{\mathcal{P}}_\alpha\varphi\big](a):=\big[P(-\zeta)\varphi\big](a)+ \int_{\zeta=\alpha}^a Q(-\zeta) \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0, 
\end{equation}
where
\[ k_R(a,a')=\sum_{j=0}^\infty \frac{R_{j}}{(j+1)!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} . \]
\color{black}
If $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
\end{lemma}

\begin{rmk}
\textcolor{pink}{For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray} \textcolor{brown}{A necessary condition for the Laplace transform to be well-defined is that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$.} \textcolor{blue}{For the Laplace transform to have any possibility of being well-defined, the ray $\Gamma_{\zeta, \alpha}^\theta$ must lie within $\domain_\alpha$.} We will see later that for our results to apply, $\domain_\alpha$ cannot touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$. As a result, $\domain_\alpha$ might look like the domain illustrated in Section \ref{setting:domain}, reinterpreting the origin as $\zeta = \alpha$. 
\end{rmk}
\begin{proof}[Proof of Lemma~\ref{lem:use-dict}]
Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we \textcolor{blue}{find that} $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$. Hence,
\begin{align*}
\mathcal{P}\Psi_\alpha & = \mathcal{P}\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha \\
& = \laplace_{\zeta,\alpha}^{\theta}\hat{\mathcal{P}}_\alpha\psi_\alpha.
\end{align*}
\end{proof}

We \textcolor{blue!50}{can} now state and prove the main result of this section. Choose a simply connected open set $\domain_\alpha$ that touches $\zeta = \alpha$ and does not touch any other roots of $P(-\zeta)$, as illustrated in Section~\ref{setting:domain} under the reinterpretation from Section \ref{sec:notation_alpha}. We will show that the Volterra equation $\hat{\mathcal{P}}_\alpha \varphi = 0$ has a unique solution of a certain form on $\domain_\alpha$. By Lemma~\ref{lem:use-dict}, the Laplace transform of this solution satisfies the equation $\mathcal{P}\Phi = 0$.
\begin{theorem}\label{thm:example}
Consider a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive. Choose a simply connected open set $\domain_\alpha$ that touches
$\zeta = \alpha$, and does not touch any other root of $P(-\zeta)$. Then the equation
\[ \hat{\mathcal{P}}_\alpha \psi_\alpha = 0 \]
has a unique solution $\psi_\alpha$ in the affine subspace
\[ \zeta^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\domain_\alpha) \]
of the space $\singexpalg{\tau_\alpha-1}(\domain_\alpha)$.
\end{theorem}
\begin{proof}[Proof of Theorem~\ref{thm:example}]
\color{red}Choose a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive. For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$, noting that $\zeta = \alpha$ is a root of $p$. The conditions laid out in Section~\ref{sec:level 1 ODE} guarantee that $\frac{\partial}{\partial \zeta} p$ and $q$ are both non-zero $\zeta = \alpha$.

>>>>

\textcolor{orange}{Integrals will typically resemble this one:}
\[ \int_{\zeta = \beta}^a \varphi\,d\zeta \]
\[ \int_b^a \varphi\,d\zeta \]

\textcolor{orange}{The integrand will always be either a 1-form, like $\varphi\,d\zeta$, or a density, like $|\varphi\,d\zeta|$. On a simply connected domain, all integration paths are equivalent, so we will typically specify an integral by its start and end points.}

In the integral
\[ \int_{\zeta = \beta}^a \big(\zeta(a) - \zeta\big)^{1/2} \varphi\,d\zeta, \]
notice that $\zeta(a)$ is a number, which stays constant throughout the integration, while $\zeta$ is a function, whose value changes along the integration path.

@@

The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$. \textcolor{blue}{When $\hardpart$ is especially regular, $\solproto$ also grows at most exponentially as $|\zeta| \to \infty$.} \textcolor{blue!50!green}{Stronger constraints on $\hardpart$ can also ensure that $\solproto$ grows at most exponentially as $|\zeta| \to \infty$.} \textcolor{pink}{With stronger constraints on $\hardpart$, \textcolor{red}{we can also ensure} \textcolor{brown}{it is guaranteed} that $\solproto$ grows at most exponentially as $|\zeta| \to \infty$.} The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
%\textcolor{Tomato}{If we change Condition \eqref{cond:sing}, it'll be enough to assume Condition \eqref{cond:diag-basic} to state Theorem \ref{thm:proto-growth}.}
\begin{theorem}\label{thm:proto-growth}
Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.

Suppose $\hardpart$ also satisfies {\em Condition~\eqref{cond:diag-basic}}. Then $f_0$ belongs to the space $\singexpalg{\tau-1}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{theorem}
We will prove this result in Section~\ref{sec:asymptotics}.
\begin{rmk}
When $\hardpart$ also satisfies Condition~\eqref{cond:reg-p}, we can get a better estimate of the prototype solution near $\zeta = 0$, as described in Proposition~\ref{prop:better-proto-estimate} from Section~\ref{sec:asymptotics}.
\end{rmk}
%
\textcolor{pink}{When we perturb $\hardpart$ to the more general operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed}, the equation we are trying to solve gets more complicated} \textcolor{brown}{For the pertubed operator $\volterra=\hardpart+\softpart$, the equation $f=\volterra f$ is more complicated, but its regular singularity at $\zeta = 0$ stays essentially the same.} \textcolor{blue}{The perturbed equation $f = \volterra f$ is more complicated, but its regular singularity at $\zeta = 0$ is essentially the same.} We might therefore expect \textcolor{pink}{to find} a solution that looks like $\solproto$ near the singularity, differing only by a less singular perturbation. If we strengthen the constraints on $\hardpart$ a little more, this expectation is fulfilled.
\begin{theorem}\label{thm:general_volterra}
Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}. Then the equation
\[ f = \volterra f \]
has a unique solution $f$ in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\gamma}(\Omega) \]
of the space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the space $\singexpalg{\tau-1}(\domain)$.

@@

Now, using Condition~\eqref{cond:sing} again, \textcolor{red}{choose some $\sigma > \tau$ and find a radius $r < \delta$} \textcolor{brown}{for a given $\sigma>0$ there exists a radius $r<\delta$} for which
\[ \left|\frac{q(a')}{p(a)}\right| < \frac{\sigma}{|\zeta(a)|} \]
whenever $|\zeta(a)| < r$ and $|\zeta(a')| < r$. Choosing a point $b'$ with $|\zeta(b')| < r$ and $q(b') \neq 0$, we \textcolor{red}{can} deduce that
\begin{align*}
|\solproto| & \lesssim \left|\frac{1}{q(b')}\right|\,\left|\frac{q(b')}{p}\right|\,|\zeta|^\tau \\
& \lesssim \left|\frac{1}{q(b')}\right|\,\frac{\sigma}{|\zeta|}\,|\zeta|^\tau \\
& \lesssim |\zeta|^{\tau-1}
\end{align*}
on the region $|\zeta| < r$, as desired.
\end{proof}
\begin{proposition}\label{prop:asymptotic at infinity}
Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}. Then $\solproto$ belongs to the space $\singexpalg{\tau-1}(\domain)$.
\end{proposition}
\begin{proof}
We want to show that $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ for some real constant $\lambda_0$.

@@

Now, \textcolor{blue}{consider} \textcolor{pink}{let us look at} the exponential factor. By Condition~\eqref{cond:sing}, \textcolor{red}{we can find} \textcolor{brown}{there exist} a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
\[ \left| \frac{q}{p}+\frac{\tau}{\zeta} \right| < C \]
in $\domain_\text{near}$. It follows that the improper integral
\[ \eta(a) = \int_{\zeta = 0}^a \left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta \]
converges for all $a \in \domain$, allowing us to write
\[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] = e^{\eta(b)} e^{-\eta(a)}. \]
Observing that $|\eta| \le C |\zeta|$ in $\near$, we conclude that
\[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] \in e^{\eta(b)} \Big[ 1 + O\big(|\zeta(a)|\big) \Big] \]
at $\zeta(a) = 0$.

@@

Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:diag-basic}}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}. Choose a subset $\far \subset \domain$ that does not touch $\zeta = 0$. Then, for any $\lambda > \lambda_\Delta$, we have

@@

\textcolor{blue}{We} again use the straight integration path $\zeta = t \zeta(a)$, with $t \in (0, 1]$. Along this path, $|\zeta(a) - \zeta| = |\zeta(a)| - |\zeta|$, allowing us to combine the exponential factors in our bound:

@@

\textcolor{red}{Let us set} \textcolor{blue}{Set} $\Lambda > \lambda$, \textcolor{blue}{so} the exponential factor shrinks as $|\zeta(a)|$ grows. Then \textcolor{red}{we can make our bound uniform} \textcolor{brown}{there is an uniform bound} over all $a \in \far$, since $|\zeta(a)| \ge \delta$ for these points:

@@

\textcolor{pink}{Now, we just want to} \textcolor{brown}{Next, we} \textcolor{blue}{Finally, we} show that the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$ for any $\rho > \tau$.

First, suppose $\rho \in (\tau, \tau+\gamma)$. In this case, we \textcolor{pink}{can} use the inclusion $\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} to see that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$. Lemma~\ref{lem:perturbed_volterra} then guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found in $\singexpalg{\tau-1+\gamma}(\Omega)$.

On the other hand, suppose $\rho > \tau+\gamma$. In this case, Proposition~\ref{prop:inclus-lt-pow-alg} gives an inclusion $\singexpalg{\rho-1}(\Omega) \hookrightarrow \singexpalg{\tau-1+\gamma}(\Omega)$. Under this inclusion, any solution of Equation~\eqref{eqn:equiv-inhomog} that we might find in $\singexpalg{\rho-1}(\Omega)$ must match the unique solution we found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
\end{proof}
\color{blue}\begin{proposition}\label{prop:alt-general_volterra}
Suppose $\volterra$ satisfies {\em Condition~\eqref{cond:reg-p}} in addition to the other assumptions of {\em Theorem~\ref{thm:general_volterra}}. Then, for each $\rho \in (\tau,\;\tau + \min\{\gamma, \epsilon, 1\}]$, the equation
\[f = \volterra f\]
has a unique solution $f$ in the affine subspace
\[ \zeta^{\tau-1}+\singexpalg{\rho-1}(\domain) \]
of the space $\singexpalg{\tau-1}(\domain)$.
\end{proposition}\color{black}
\begin{proof}
Propositions \ref{prop:asymptotic at infinity} and \ref{prop:better-proto-estimate} imply that for some constant $M$,
\[ \zeta^{\tau-1} + \singexpalg{\rho-1}(\domain) = M^{-1}\solproto + \singexpalg{\rho-1}(\domain) \]
whenever $\rho \le \tau + \min\{\epsilon, 1\}$. Theorem~\ref{thm:general_volterra} implies that our equation has a unique solution in
\[ M^{-1}\solproto + \singexpalg{\rho-1}(\domain) \]
as long as $\rho \in (\tau, \tau + \gamma]$. Putting these facts together, we get the desired result.
\end{proof}
\section{A motivating example}\label{sec:example}
\subsection{Overview}
We can use our \textcolor{pink}{understanding} \textcolor{blue}{analysis} of regular singular Volterra equations to study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$. \textcolor{pink}{In particular} \textcolor{blue}{Under certain conditions}, we \textcolor{blue!50}{can} build a set of analytic solutions in the frequency domain by solving certain regular singular Volterra equations in the position domain. Our main results guarantee that these position domain solutions exist, are unique, and have well-defined Laplace transforms.
\subsection{Level $1$ differential equations}\label{sec:level 1 ODE}
Let $\mathcal{P}$ be a linear differential operator of the form
\[ \mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}), \]
where
\begin{enumerate}
\item[$\bullet$] $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial that is non-zero at every root of $P$;
\item[$\bullet$] $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
\[ R(z^{-1}) = \sum_{j=0}^\infty R_j z^{-j} \]
converges in the region $|z| > A$.
\end{enumerate}
Equations of the form $\mathcal{P}\Phi = 0$ are a sub-class of what Ecalle calls {\em level~1} differential equations~\cite[Section~2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}. In an upcoming paper \cite{borel_reg}, we will study various examples of such equations using Laplace transform methods, with the help of our existence and uniqueness result Theorem~\ref{thm:general_volterra}. 
\subsection{Notation}\label{sec:notation_alpha}
So far, we have studied a Volterra equation with a regular singularity at $\zeta = 0$. When we use Laplace transform methods to solve a level~1 differential equation $\mathcal{P}\Phi = 0$ in the frequency domain, we will end up with several Volterra equations $\hat{\mathcal{P}}_\alpha \varphi = 0$ in the position domain, each with a regular singularity at a different root $\zeta = \alpha$ of the polynomial $P(-\zeta)$.

@@

\begin{rmk}
In the relationship between $\fracderiv{-\nu}{\zeta}{\alpha}$ and multiplication by $z^{-\nu}$ described above, smoothing out the singularity at $\zeta = \alpha$ in the position domain corresponds to speeding up the decay as $|z| \to \infty$ in the frequency domain. This is a general feature of the Laplace transform.
\end{rmk}
\subsection{Going to the position domain}
\textcolor{blue}{Under the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$, differential operators on the frequency domain pull back to integral operators on the position domain.}
\textcolor{pink}{Using the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ \textcolor{red}{we can turn} differential operators in the frequency domain into \textcolor{blue}{integral} operators in the position domain.}
\begin{lemma}\label{lem:use-dict}
For \textcolor{blue}{any $\alpha \in \C$}, let $\hat{\mathcal{P}}_{\alpha}$ be the \textcolor{blue}{integral} operator 
\[ \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1}). \]
If $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
\end{lemma}
\begin{rmk}
\textcolor{pink}{For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray} \textcolor{brown}{A necessary condition for the Laplace transform to be well-defined is that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$.} \textcolor{blue}{For the Laplace transform to be well-defined, $\domain_\alpha$ must contain the ray $\Gamma_{\zeta, \alpha}^\theta$ as a necessary condition.} We will see later that for our results to apply, $\domain_\alpha$ \textcolor{blue}{also} cannot touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$. As a result, $\domain_\alpha$ might look like the domain illustrated in Section \ref{setting:domain}, reinterpreting the origin as $\zeta = \alpha$. 
\end{rmk}
\color{blue}\begin{rmk}\label{rmk:use-dict-explicit}
To write $\hat{\mathcal{P}}_\alpha$ more explicitly, let $p := P(-\zeta)$ and $q := Q(-\zeta)$, noting that $\zeta = \alpha$ is a root of $p$. Then
\[ \big[\hat{\mathcal{P}}_\alpha\varphi\big](a) = \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta, \]
where
\[ k_R(a,a') := \sum_{j=0}^\infty \frac{R_{j}}{(j+1)!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} . \]
\end{rmk}\color{black}
\begin{proof}[Proof of Lemma~\ref{lem:use-dict}]
Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we \textcolor{blue}{find that} $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$. Hence,
\begin{align*}
\mathcal{P}\Psi_\alpha & = \mathcal{P}\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha \\
& = \laplace_{\zeta,\alpha}^{\theta}\hat{\mathcal{P}}_\alpha\psi_\alpha.
\end{align*}
\end{proof}
